Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/RMPC_Daisy.tex
renaming section to background
Added conclusion. Fixed Fig 3.

% !TEX root = main.tex
\section{Explicit MPC and Finite Precision}
In this section, we provide relevant background on robust explicit MPC,
fixed-point arithmetic and error analysis.

@@

\begin{theorem}[\cite{delaPea:2005}]
The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution. Furthermore, for the case that $R>0$, the controller is $u_k = K x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
\kappa(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
\end{theorem}
The essential idea behind this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
%\begin{align}
%	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
%	&s.t.\quad JU_N\leq s+Dx_0
%\end{align} 
\begin{align}
\label{eq:multi_param_prog}
J^{\ast}(x_0)=\min_{z,\gamma}& \left[x_0^TYx_0+\frac{1}{2}z^THz+\gamma\right]\\
\text{s.t.} \quad &G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
&G_cz\leq W_c+S_cx_0\nonumber
\end{align}
where, $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables and $Y$, $H$, $G_m$, $G_c$,$S_m$, $S_c$, $W_m$, $W_c$, $g_m$ are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).

@@

%Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. The most straightforward technique is a linear search over all polyhedral region in \statespace\space using a switch/case conditional statement as shown in~\autoref{lst:caseof}.
%\Sadegh{Perhaps we can mention another approach here? add references.}

\begin{figure}[t]
\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={switch, case, then}]
switch($\statevar$):
  case ($H_{1}\statevar<=K_{1}$) then ($v_{k}=F_1x_k+G_1$)
  case ($H_{2}\statevar<=K_{2}$) then ($v_{k}=F_2x_k+G_2$)
  case ($H_{3}\statevar<=K_{3}$) then ($v_{k}=F_3x_k+G_3$)
    ...
  case ($ H_{P}\statevar<=K_{P}$) then ($v_{k}=F_Px_k+G_P$)
\end{lstlisting}
\caption{Structure of an explicit MPC controller}
\label{lst:caseof}
\end{figure}
%Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.

>>>>

% !TEX root = main.tex
\section{Background}
In this section, we provide relevant background on robust explicit MPC,
fixed-point arithmetic and error analysis.

@@

\begin{theorem}[\cite{delaPea:2005}]
The optimization \eqref{eq:RMPC_prob} can be translated into a multi-parametric quadratic problem which admits a closed-form solution. Furthermore, for the case that $R>0$, the controller is $u_k = K x_k + \kappa(x_k)$ with $\kappa(\cdot)$ being a continuous piecewise affine (PWA) function over polyhedral regions:
\begin{equation}
\kappa(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a polyhedral region determined by a set of linear inequalities $\mathcal R_i = \{x\in\mathcal X\,|\,H_ix\leq K_i\}$. 
\end{theorem}
The essential idea behind this theorem is to utilize the closed form $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$ and transform the optimization \eqref{eq:RMPC_prob} into the following quadratic program:
%\begin{align}
%	&\min_{U_N}U_N^TZU_N+x_0^TVU_N+x_0^TYx_0\nonumber\\
%	&s.t.\quad JU_N\leq s+Dx_0
%\end{align} 
\begin{align}
\label{eq:multi_param_prog}
J^{\ast}(x_0)=\min_{z,\gamma}& \left[x_0^TYx_0+\frac{1}{2}z^THz+\gamma\right]\\
\text{s.t.} \quad &G_mz+g_m\gamma\leq W_m+S_mx_0,\nonumber\\
&G_cz\leq W_c+S_cx_0\nonumber
\end{align}
where $z\in \reals^{mN}$ and $\gamma\in\reals$ are decision variables, and $Y$, $H$, $G_m$, $G_c$, $S_m$, $S_c$, $W_m$, $W_c$, and $g_m$ 
are matrices of proper sizes that can be easily obtained from the original optimization \eqref{eq:RMPC_prob}  (see \cite{delaPea:2005}).

@@

%Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong.
Several algorithms are proposed in the literature \cite{Mnnigmann:2011,Jones:2006} to find the right polyhedral region $i$ to which the state $x_k$ belong. 
The most straightforward technique is a linear search over all polyhedral regions (Fig.~\ref{lst:caseof}).

\begin{figure}[t]
\begin{lstlisting}[mathescape=true,basicstyle=\small\ttfamily,morekeywords={if, then, elseif, return}]
if ($H_{1}\statevar \leq K_{1}$) then $v_{k}=F_1x_k+G_1$
elseif ($H_{2}\statevar \leq K_{2}$) then $v_{k}=F_2x_k+G_2$
elseif ($H_{3}\statevar \leq K_{3}$) then $v_{k}=F_3x_k+G_3$
...
elseif ($ H_{P}\statevar\leq K_{P}$) then $v_{k}=F_Px_k+G_P$
return $v_k$
\end{lstlisting}
\caption{Structure of an explicit MPC controller}
\label{lst:caseof}
\end{figure}
%Once the polytope was determined, computing for $F_ix+G_i$ requires even less effort as it only involves summation and multiplication.
